---
output: 
  html_document:
    keep_md: yes
---


## Loading and preprocessing the data
```{r}
input1 <- read.csv("D:/Users/kamatchi/Documents/Reproducible Research/Week2 Lectures/Week2 assignment/activity.csv")
df<- NULL
dftest<- NULL
dftest1<- NULL
```


## What is mean total number of steps taken per day?
##Subset first for each day and add steps for each day
## plot histogram
## calculate median and mean
```{r}
test2<- unique(input1$date)
for(i in 1:length(test2)){
  j<- test2[i]
  dftest<- subset(input1, input1$date==j)
  sumsteps <- sum(dftest$steps, na.rm=TRUE)
  dftest1<- cbind.data.frame(j, sumsteps) 
  df<-rbind(df,dftest1)
}
names(df)<-c("date", "sumsteps")
hist(df$sumsteps)
a<- median(df$sumsteps)
a
b<- mean(df$sumsteps)
b
```


## What is the average daily activity pattern?
## Subset first for each five minute interval 
## and calculate the mean for each interval
## plot time series plot 
## find the maximum value of the mean
## subset to find the interval that has the maximum
```{r}
df2<- NULL
df2test<-NULL
df2test1<-NULL
df2test2<-NULL
test3<-unique(input1$interval)
for (i in 1:length(test3)){ 
  k<-test3[i]
  df2test<- subset(input1, input1$interval==k)
  meansteps1 <- mean(df2test$steps, na.rm=TRUE)
  df2test1 <- cbind.data.frame(k, meansteps1)
  df2<-rbind(df2, df2test1)
}
names(df2)<- c("interval", "meansteps")
plot(df2$interval, df2$meansteps, type="l")
b1<-max(subset(df2, select=meansteps))
df2test2<-subset(df2, df2$meansteps==b1)
df2test2
```


## Imputing missing values
## Calculate the number of rows with NA
```{r}
b3<-sum(is.na(input1$steps))
b3
```
## Try to replace the NA values with mean for the same 5 minute 
## interval. Then calculate median and mean
## from results we can say that there is no difference found by 
## replacing the NA with mean values as far as mean and median. 
```{r}
df3test<-subset(input1, is.na(input1$steps))
df3test1<-input1[complete.cases(input1),]

for (i in 1:nrow(df3test)){
  if (df3test$interval %in% df2$interval){ 
    df3test$steps<- df2$meansteps
  }
}
df3test1<-rbind(df3test1,df3test)
df3test1
df3<-NULL
for(i in 1:length(test2)){
  j<- test2[i]
  df3test2<- subset(df3test1, df3test1$date==j)
  sumsteps3 <- sum(df3test2$steps, na.rm=TRUE)
  df3test3<- cbind.data.frame(j, sumsteps3) 
  df3<-rbind(df3,df3test3)
}
names(df3)<-c("date", "sumsteps")
hist(df3$sumsteps)
a1<- median(df$sumsteps)
a1
b1<- mean(df$sumsteps)
b1
```



## Are there differences in activity patterns between weekdays and weekends?
 first sort out days in input2 as weekdays or weekend
 prior to that we have to change the format to get into appropriate
 format for weekdays() to read it. 
## COuld not get this part to work..

